This is an example of article title

### 2019-08-13 paper/paper.tex

This study has four core sections. The first surveys what are some commonly used functionality for econometrics analysis. The second provides an overview of the current state of these within the Julia ecosystem including current tools and gaps. The third provides a comprehensive summary of the functionality provided by the new package, Econometrics.jl, and next steps. Lastly, I provide insights on how the Julia ecosystem can evolve from my experience developing the new tool.

Regression analysis is a core tool used to understand the relation among variables. For example, understanding these relationships can provide insights into causal relations or as a basis to develop predictive models. In the realm of statistical inference from regression analysis, one may be interested in common targets such as confidence intervals of the parameters estimates, joint-significance of features, out-of-sample predictive performance, and others. Moreover, most models make certain assumptions which can be tested through statistical tests or model diagnostics which provide confidence in the estimation and results.

@@

Out of the many potential tools practitioners may require, what are some of the most common? Not every estimator is as widely accessible or commonly used. Some educated guesses may be well justified such as ordinary least squares being more widely used than spatially-weighted regressions. In order to avoid speculation, I defer to a reasonable assumption that the most common estimators are those usually taught in academic programs and available in widely used software \cite{Renfro_2009}. Most programs teach tools to address the most common response types: continuous, count / rates, nominal, ordinal, and duration outcomes. This suggests some common models may include linear models, Poisson/negative binomial, multinomial logistic regression, and ordinal logistic regression with proportional odds assumption. Topics in time series and panel data are usually offered in most programs. Perhaps, the most common topic is short panels (i.e., many units of observations and relatively small number of repeated observations). Common estimators include pooling, first-difference, fixed effects / within estimator, and one-way random effects. The between estimator is usually masked as an intermediate model for estimating the error component in the random effects model. Lastly, the two big challenges taught in most programs are endogeneity and heteroscedasticity. These challenges are usually countered through instrumental variables (e.g., 2SLS) or robust variance-covariance estimators (e.g., heteroscedasticity consistent estimators).

@@

The Julia language \cite{Bezanson_Edelman_Karpinski_Shah_2017} is an upcoming language especially well-suited for scientific computing such as econometrics, data science, machine learning, and other related tasks.

@@

StatsBase.jl builds on top of Statistics.jl (standard library) to provide additional statistical functionality. One which includes the abstraction for Statistical Models (and Regression models which inherits from the former). It provides a simple and powerful API for the whole Julia ecosystem to use. It allows packages to implement the API and easily support a common functionality users can expect and interact with in a familiar manner. For example, \textit{coef} will extract the parameter estimates from any object that implements the API. The full API include model statistics such as: coefficient of determination (or adjusted), information criteria statistics such as AIC/BIC (and corrected), statistics about the model fitness such as deviance, log-likelihood, and usual queries such as point estimates, variance covariance estimates, standard errors, confidence intervals, degrees of freedom (or residual degrees of freedom), etc. Lastly, several accessors are available for fitted values, response, model matrix, information matrix, leverage values, error components, etc. Lastly, it also provides an abstraction for weights including frequency weights and analytical weights.

@@

Software analysis should always include diagnostics and tools to make it easier for dissemination. Many tests and diagnostics are applicable to a wide set of implementations. The best manner to make these available and for these to ``play nicely'' with one another is to have an effective API. Sadly, the Julia ecosystem has yet to experience wide adoption of this pattern. For example, packages might need to access components for computing a test or providing some estimates such as variance covariance estimates. The test might include components such as the residual degrees of freedom, the information matrix, residuals, and score. Currently, some packages rely on accessing internal components specific to those implementations rather than an implementation agnostic interface. A common public API would also allow to catch context specific instances of improper behavior.

Various decisions are software specific with asymptotic justification, but significant finite-sample consequences. Software may differ on whether to report statistics using finite-sample statistics (t-distribution, F-distribution) or asymptotic equivalent counterparts (Normal, Chi squared). These tend to have negligible effect in most applications, but other decisions such as degrees of freedom may have larger consequences. For example, software may differs on how it computes the degrees of freedom for instrumental variables or absorbed variables depending on the context (e.g., main regression or auxiliary regression for estimating error components). Refinements and robustness checks can also contribute to a better analysis such as verifying gaps for time variant operations such as in first-difference or purging singletons and other degree of freedom adjustments \cite{Singletons}.

>>>>

This study has four core sections. The first surveys what are some commonly used functionality for econometrics analysis. The second provides an overview of the current state of these within the Julia \cite{Bezanson_Edelman_Karpinski_Shah_2017} ecosystem including current tools and gaps. The third provides a comprehensive summary of the functionality provided by the new package, Econometrics.jl, and next steps. Lastly, I provide insights on how the Julia ecosystem can evolve from my experience developing the new tool.

Regression analysis is a core tool used to understand the relation among variables. For example, understanding these relationships can provide insights into causal relations or as a basis to develop predictive models. In the realm of statistical inference, one may be interested in common targets such as confidence intervals of the parameters estimates, joint-significance of features, out-of-sample predictive performance, and others. Moreover, most models make certain assumptions which can be tested through statistical tests or model diagnostics which provide confidence in the estimation and results.

@@

Of the many potential tools practitioners may require, what are some of the most common? Not every estimator is as widely accessible or commonly used. Some educated guesses may be well justified such as ordinary least squares being more widely used than spatially-weighted regressions. In order to avoid speculation, I defer to a reasonable assumption that the most common estimators are those usually taught in academic programs and available in widely used software \cite{Renfro_2009}. Most programs teach tools to address the most common response types: continuous, count / rates, nominal, ordinal, and duration outcomes. This suggests some common models may include linear models, Poisson/negative binomial, multinomial logistic regression, and ordinal logistic regression with proportional odds assumption. Topics in time series and panel data are usually offered in most programs. Perhaps, the most common topic is short panels (i.e., many units of observations and relatively small number of repeated observations). Common estimators include pooling, first-difference, fixed effects / within estimator, and one-way random effects. The between estimator is usually masked as an intermediate model for estimating the error component in the random effects model. Lastly, the two big challenges taught in most programs are endogeneity and heteroscedasticity. These challenges are usually countered through instrumental variables (e.g., 2SLS) or robust variance-covariance estimators (e.g., heteroscedasticity consistent estimators).

@@

@@

StatsBase.jl builds on top of Statistics.jl (standard library) to provide additional statistical functionality. One which includes the abstraction for Statistical Models (and Regression models which inherits from the former). It provides a simple and powerful API for the whole Julia ecosystem to use. It allows packages to implement the API and easily support a common functionality users can expect and interact with in a familiar manner. For example, \textit{coef} will extract the parameter estimates from any object that implements the API. The full API include model statistics such as: coefficient of determination (or adjusted), information criteria statistics such as AIC/BIC (and corrected), statistics about the model fitness such as deviance, log-likelihood, and usual queries such as point estimates, variance covariance estimates, standard errors, confidence intervals, degrees of freedom (or residual degrees of freedom). Lastly, several accessors are available for fitted values, response, model matrix, information matrix, leverage values, error components, etc. Lastly, it also provides an abstraction for weights including frequency weights and analytical weights.

@@

The decision to adhere to a common API has various benefits. For example, being able to interact and query models consistently enables packages that enhance the experience providing features such as diagnostics (i.e., statistical tests, plots) or convenience tools for dissemination such as \LaTeX\ code for results. Currently, the ecosystem still demands certain functionality to rely on internals which forces code to be less generalizable (e.g., CovarianceMatrices.jl only supports GLM models and relies on internals rather than a common API).

Econometrics.jl has as a goal to make opinionated decisions after careful consideration. Consider for example whether to report statistics using finite-sample statistics (t-distribution, F-distribution) or asymptotic equivalent counterparts (Normal, Chi squared). These tend to have negligible effects in most applications, but other decisions such as degrees of freedom may have larger consequences. One case is how software computes the degrees of freedom for instrumental variables or absorbed variables depending on the context (e.g., main regression or auxiliary regression for estimating error components). Refinements and robustness checks can also contribute to a better analysis such as verifying gaps for time variant operations such as in first-difference or purging singletons and other degree of freedom adjustments \cite{Singletons}.
